Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-10-25 paper/main.tex
More text on Tahoe architecture

\subsection{Erasure coding}

The use of \emph{erasure coding} enables Tahoe to recover a file using only a
predefined subset of the parts distributed to the storage servers, i.e. the
other nodes in the grid. Erasure coding is a type of \ac{FEC} code, which
extends a message with $C$ characters into a longer message with $N$ symbols.
The original $C$ characters can then be recovered from a subset of the $N$
symbols.

The properties of erasure coding can be seen up on as those of recovery in RAID
systems.

% TODO: comparison with RAID?

@@

% Describe hash trees in further detail?

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{Tahoe-hashing.pdf}
    \caption{Tahoe-LAFS: Location of hashing}
    \label{fig:tahoehashing}
\end{figure}

>>>>

\subsection{Architecture}

Tahoe has a three layer architecture: the key-value store, the filesystem, and
the application.

The \textbf{key-value store}, or the ``capability-data bytes'' store, is the
lowest layer and is implemented by a grid of Tahoe-LAFS storage servers. Data is
kept on the storage servers in the form of ``shares'', which are encrypted and
encoded parts of files. Capabilities are short ASCII strings, containing
information on where to \emph{find} a file, and how to \emph{verify} it.
Nodes in the grid learn about each other through an ``introducer'', which
roughly relates to a tracker in the BitTorrent\footnote{See
\url{http://www.bittorrent.org/beps/bep\_0003.html}} protocol.

The \textbf{filesystem} layer is responsible for mapping human-meaningful
pathnames to pieces of data. Each directory contains a table of capabilities
for its children, i.e. subdirectories or files. Two forms of capabilities is
available for each file, read-only and read-write, and these can be shared to
provide shared/published directory structures with friends.

Since it is not practical for users to remember strings containing random
characters, the \textbf{application} layer is used for providing a user-friendly
interface to the directories and files.

\subsection{Related technologies}

Tahoe-\ac{LAFS} uses a number of techniques to realize the functionality
demanded by a secure, distributed filesystem.

\paragraph{Erasure coding.}

When a client puts a file on the grid, it first encrypts the file, before
breaking the file into small segments. The segments are then erasure coded.
The use of \emph{erasure coding} enables Tahoe to recover a file using only a
predefined subset of the parts distributed to the storage servers, i.e. the
other nodes in the grid. Erasure coding is a type of \ac{FEC} code, which
extends a message with $C$ characters into a longer message with $N$ symbols
\cite{t_reed-solomon}.
The original $C$ characters can then be recovered from a subset of the $N$
symbols.

The properties of erasure coding can be seen up on as those of recovery in RAID
systems. \cite{t_erasure} % TODO: comparison with RAID

\paragraph{Merkle hash trees.}

Describe hash trees in further detail?

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\columnwidth]{Tahoe-hashing.pdf}
    \caption{Tahoe-LAFS: Location of hashing}
    \label{fig:tahoehashing}
\end{figure}
